### 2020-09-08 proposals/benefit-of-collaboration/benefit-of-collaboration.tex

\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough
\usepackage{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{subfig}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}}
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{times}
\usepackage{enumitem}
\usepackage{float}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{tabulary}
%\usepackage[labelfont=bf]{caption}

@@

\usepackage{wrapfig}
\setlength{\intextsep}{0.20mm}
\setlength{\columnsep}{0.20mm}

@@

\begin{filecontents}{references.bib}
\end{filecontents}

@@

{\centering 
    \textbf{Title\\
    Call \\
    }
    Name (PI) - Affiliation\\
    Name (co-PI) - Affiliation 
\par
}
\vspace{\baselineskip}

@@

%\begin{wrapfigure}{l}{0.32\textwidth}
%    \includegraphics[width=0.30\textwidth]{}
%    \captionsetup{justification=centering}
%    \caption{WSC simulator.}
%    \label{fig-wsc-simulator}
%\end{wrapfigure}
\noindent 
\\
\noindent\textbf{Motivation.} \textit{Context.}

\noindent\textbf{Overall Objective.} The overall objective of this project is to 
\\

\noindent\textbf{Research Focus.} The N workscopes in this project are - 
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item\textit{Title (Lead - )}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item
            \item
        \end{itemize}
\end{enumerate}

@@

\noindent\textbf{Importance and Relevance to Objectives.} \textit{Background.}

\textit{Relevant literature.}

\textit{Unique project features.} 
\\

\noindent\textbf{Logical Path, Work Scope, Description of Tasks.} The Logical Path and the proposed Work Scope is described below in terms of the defined Tasks for the project. Many of the Tasks overlap. Research will be concurrent and mutually dependent across the investigators.\\

\noindent\textbf{Workscope 1. Task I. Title.} (\textit{Lead - ; Support - }) 
\\

\noindent\textbf{Workscope N. Task X. Crosscutting Issues.} (\textit{Lead - PI; Support - All}) Lessons learned will be identified for project outcomes. Additional discussion will cover -
\begin{itemize}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item
\end{itemize}

\noindent\textbf{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} We anticipate the following outcomes -
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item
\end{enumerate}

\begin{table}[H]
    \centering
    \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
    \begin{tabular}{|p{0.27\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
        \hline
        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}& 
        \multicolumn{4}{|c|}{\textbf{Y1}}&
        \multicolumn{4}{|c|}{\textbf{Y2}}&
        \multicolumn{4}{|c|}{\textbf{Y3}}\\
        \cline{2-13}
        &
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}\\
        \hline
        I. 
        &\x\textbf{I} 
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        & \\
        \hline
        II. 
        &\x\textbf{II} 
        &
        &
        &
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & \\
        \hline
        III. 
        &\x\textbf{III} 
        &
        &
        &
        &
        &
        & 
        & 
        & 
        & 
        & 
        & \\
        \hline
        IV. 
        &\x\textbf{IV} 
        & 
        & 
        &
        &
        &
        &
        & 
        & 
        & 
        & 
        & \\
        \hline
        V. 
        &\x\textbf{V} 
        & 
        & 
        &
        &
        &
        &
        &
        &
        &
        &  
        & \\
        \hline
        VI. 
        &\x\textbf{VI} 
        & 
        & 
        & 
        & 
        & 
        &
        &
        &
        &
        & 
        & \\
        \hline
        VII. Crosscutting issues 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        &
        &\x\textbf{VII}
        &\x\textbf{VII} \\
        \hline
    \end{tabular}
    \label{tab-timeframe}
\end{table}

\begin{table}[H]
    \centering
    \caption*{\textbf{Milestones.}}
    \begin{tabular}{|l|l|l|}
        \hline
        \multicolumn{1}{|c|}{\textbf{Milestone}}
        &\multicolumn{1}{|c|}{\textbf{Deliverable}}
        &\multicolumn{1}{|c|}{\textbf{Completion}}\\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        0. Project\\logistics
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        0.1. Kick-off report, roles, and responsibilities.\\
        0.2. Annual reports.\\
        0.3. Agency administrative requirements.\\
        0.4. Final project report.\\
        0.5. Journal paper submission.\\
        0.6. Professional society conference presentations.
        \end{tabular}
        & 
        \begin{tabular}[c]{@{}l@{}}
        0.1. Y1-Q2\\
        0.2. Annually\\
        0.3. Quarterly\\
        0.4. Y3-Q4\\
        0.5. Annually\\
        0.6. Annually
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        1. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        1.1. \\
        1.2. \\
        1.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        1.1. \\
        1.2. \\
        1.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        2. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        2.1. \\
        2.2. \\
        2.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        2.1. \\
        2.2. \\
        2.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        3.1. \\
        3.2. \\
        3.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        3.1. \\
        3.2. \\
        3.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        4. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        4.1. \\
        4.2. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        4.1. \\
        4.2. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        5. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        5.1. \\
        5.2  \\
        5.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        5.1. \\
        5.2. \\
        5.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        6. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        6.1. \\
        6.2. \\
        6.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        6.1. \\
        6.2. \\
        6.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        7. Discuss\\crosscutting\\issues
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        7.1. Identify lessons learned.\\
        7.2. Develop future research and educational pathways.
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        7.1. Y3-Q3\\
        7.2. Y3-Q4
        \end{tabular}
        \\
        \hline
    \end{tabular}
    \label{tab-milestones}
\end{table}

\noindent\textbf{Contribution to Advancing State of the Art in Nuclear Engineering and Cybersecurity.} 
\\

\noindent\textbf{Description of Facilities to be Utilized to Execute Scope.} 
\\

\noindent\textbf{Challenges to Accomplish Tasks and Planned Mitigations.} 
\\

\begin{table}[H]
    \centering
    \begin{tabular}{|p{0.45\linewidth}|p{0.45\linewidth}|}
        \hline
        \multicolumn{1}{|c|}{\textbf{Challenges to accomplish tasks}}
        &\multicolumn{1}{|c|}{\textbf{Planned mitigations}}\\
        \hline

        & \\
        \hline

        & \\
        \hline

        & \\
        \hline

        & \\
        \hline

        & \\
        \hline
    \end{tabular}
    \label{tab-milestones}
\end{table}

\noindent\textbf{Information, Data, and Plans.} All information has been presented in the technical scope.\\

\noindent\textbf{Quality Assurance.} Our project team have practiced a QA approach, consistent with the graded approach established by the DOE Technical Integration Office, per the NEUP website and any additional requirements deemed necessary during contracting. All projects undergo safety review by experts. We have followed this QA expectation in all ongoing awards.\\

\noindent\textbf{Mandatory Requirements.} We abide by current and pending information on nuclear-related federal funding contained in Form 3204. The Mandatory, Go/No-go, requirements will be coordinated with the institutional Office of Sponsored Research, the general counsel, and the Office of Technology Transfer. Each PI noted below will assume responsibility as the point of contact.\\

\begin{table}[h!]
    \centering
    \begin{tabular}{|c|c|c|c|}
        \hline
        \textbf{No.}
        &\textbf{Requirement}
        &\textbf{Responsibility}
        &\textbf{Evaluation}\\
        \hline
        1
        &Commitment to reporting and budget requirements
        &All PIs
        &Go/No-go \\
        \hline
        2
        &10 CFR 851 Worker Safety and Health Program
        &All PIs
        &Go/No-go \\
        \hline
        3
        &Export Control
        &All PIs
        &Go/No-go \\
        \hline
        4
        &Standard Research Subcontract
        &All PIs
        &Go/No-go \\
        \hline
        5
        &Quality Assurance
        &All PIs
        &Go/No-go \\
        \hline
        6
        &Commitment to prepare additional contract elements
        &All PIs
        &Go/No-go \\
        \hline
    \end{tabular}
    \label{tab-mandatory-requirements}
\end{table}

\noindent\textbf{References}
\bibliographystyle{neup}
\setlength{\bibhang}{0pt}
\bibliography{references}

>>>>

\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough
\usepackage{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{subfig}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}}
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{times}
\usepackage{enumitem}
\usepackage{float}
\usepackage{multirow}
%\usepackage[labelfont=bf]{caption}

@@

\usepackage{wrapfig}
\setlength{\intextsep}{0.10mm}
\setlength{\columnsep}{0.10mm}

@@

@@

{\centering 
    \textbf{BENEFIT OF COLLABORATORS\\
    Title\\
    Call\\
    }
    Name (PI) - Affiliation\\
    Name (co-PI) - 
\par
}

@@

\noindent\textbf{Motivation.}

\noindent\textbf{Research Focus.} The N workscopes in this project are - 
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item\textit{Title (Lead - )}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item 
            \item 
        \end{itemize}
    \item\textit{Crosscutting Issues (Full team)}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item Identify lessons learned
            \item Develop future research pathways
        \end{itemize}
\end{enumerate}

@@

\noindent\textbf{Team.} This research will facilitate collaboration among current industry experts with extensive \textit{fill in phrase about team expertise.} The project team consists of the following members. The contribution of each is noted. The corresponding facilities are briefly described thereafter.
\\

\noindent\textbf{Prof./Dr. Name} (Ph.D., Degree Granting Institution) is a \textit{title} at \textit{Affiliation}, etc. His/Her/Their research focus is in \textit{area of expertise}. Prof./Dr. Name is the PI of this project and will be responsible for progress and achievement of all objectives, tasks, and deliverables. He/She/They has expertise in \textit{topics contained in text of narrative} from \textit{where/how this expertise was acquired}. He/She/They teach \textit{relevant courses} at \textit{Affiliation}.
\\

\noindent\textbf{Prof./Dr. Name} (Ph.D., Degree Granting Institution) is a \textit{title} at \textit{Affiliation}, etc. His/Her/Their research focus is in \textit{area of expertise}. Prof./Dr. Name is the co-PI of this project and will contibute expertise in \textit{related project tasks}. He/She/They also is/was \textit{related experience} from \textit{where/how this expertise was acquired}. He/She/They teach \textit{relevant courses} at \textit{Affiliation}.
\\

\noindent\textbf{Important Research Facility/Equipment} is \textit{description as relevant to project.}
\\

\noindent\textbf{Work Project Documentation, Quality Control.} The co-PIs have practiced a QA approach, consistent with that established by the DOE Technical Integration Office, per NEUP website and any additional requirements deemed necessary during contracting. All projects undergo safety review by experts. We have followed this QA expectation in all ongoing awards. We abide by current and pending information on nuclear-related federal funding contained in Form 3204. The Mandatory, Go/No-go, requirements will be coordinated with UI’s Office of Sponsored Research, the general counsel and Technology Transfer. The PIs assume responsibility as the POC and follow these requirements: 1) Commitment to reporting and budget requirements, 2) 10CFR851 Worker Safety and Health Program, 3) Export Control and 4) Quality Assurance.
\\
